%-------------------------
% Resume in Latex
% Author : Harshibar
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underline
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% SAFE TOP-PADDING REMOVAL (ELIMINATES THE TOP GRAY GAP)
\setlength{\headheight}{0pt}
\setlength{\headsep}{0pt}
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-0.75in} 
\addtolength{\textheight}{1.3in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section headings
\titleformat{\section}{
    \bfseries\vspace{-4pt}\raggedright\large
}{}{0em}{}[\color{light-grey}{\titlerule[1.5pt]}\vspace{-4pt}]

% Precise formatting layout definitions
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-1.5pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2.5pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{0.5pt}\\
      \textit{\small#3} & {\color{dark-grey} \small #4}\\
    \end{tabular*}\vspace{-5.5pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2.5pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}\small #2} \\
    \end{tabular*}\vspace{-5.5pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-3pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, itemsep=1.2pt, parsep=0pt, topsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-1pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\renewcommand{\baselinestretch}{0.96}\selectfont

%----------HEADING (SHIFTED UP PERFECTLY)----------
\begin{center}
    \textbf{\Huge Mihir Bachhav} \\ \vspace{2pt}
    \small 
    \faPhone* \hspace{2pt} \href{tel:+919112018504}{\texttt{+91 9112018504}} \hspace{5pt} $|$ \hspace{5pt}
    \faEnvelope \hspace{2pt} \href{mailto:mihirbachhav025@gmail.com}{\texttt{mihirbachhav025@gmail.com}} \hspace{5pt} $|$ \hspace{5pt}
    \faLinkedin \hspace{2pt} \href{https://www.linkedin.com/in/mihir-b-240519191/}{\texttt{mihir\_bachhav}} \hspace{5pt} $|$ \hspace{5pt}
    \faMapMarker* \hspace{1pt} \texttt{Mumbai, India}
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

   \resumeSubheading
{GEP Worldwide}{June 2023 -- Sept. 2025}
{Software Engineer - Data Platform}{Mumbai, Maharashtra}
\resumeItemListStart

    \resumeItem{\textbf{Re-engineered enterprise reporting workloads} from SQL Server to Azure Databricks using the Medallion Architecture and an internally developed Audit-Balance-Control (ABC) framework, enabling scalable Spark-based analytics and reporting.}

    \resumeItem{\textbf{Optimized large-scale reporting pipelines} and data processing workloads in Azure Databricks, reducing execution times for critical reporting jobs by up to \textbf{50\%}.}

    \resumeItem{\textbf{Built and maintained Power BI semantic models}, tabular models, and DAX measures supporting enterprise reporting and analytics requirements.}

    \resumeItem{\textbf{Owned Dataplatform platform operations}, including production release cycles, production support, escalation management, ticket triage, and facilitation of Agile Scrum ceremonies.}

    \resumeItem{\textbf{Led reporting backend migrations} from GEP Smart (SQL Server) to GEP Quantum (MongoDB), reducing migration setup time from \textbf{7 days to 2 days} through automation utilities and standardized migration workflows.}

    \resumeItem{\textbf{Designed metadata-driven migration frameworks} that leveraged configuration data and domain models to automate reporting setup, schema reconciliation, and client onboarding with minimal manual intervention.}

    \resumeItem{\textbf{Implemented intelligent schema and column-mapping solutions} to bridge reporting differences between legacy and next-generation platforms while preserving existing client reporting experiences.}

    \resumeItem{\textbf{Developed automated report validation and data-quality frameworks} supporting \textbf{500+ reports}, \textbf{100+ clients}, and \textbf{12+ business modules} during large-scale platform migrations.}

    \resumeItem{\textbf{Partnered with product, technology service, implementation, and client teams} to design custom reporting solutions and translate complex business requirements into scalable reporting architectures.}

    \resumeItem{\textbf{Designed and delivered Project Savings reporting transformations}, enabling highly customized client reporting requirements through a reusable metadata-driven reporting framework.}

    \resumeItem{\textbf{Mentored new team members}, contributed to ABC platform enhancements, resolved production-critical defects, and drove continuous improvements to reporting infrastructure.}

  \resumeItemListEnd

    \resumeSubheading
      {CogXr Labs}{Sep. 2022 -- Mar. 2023}
      {Software Developer Intern}{Remote, India}
      \resumeItemListStart
        \resumeItem{\textbf{Built responsive UI screens using Flutter}, ensuring seamless cross-platform design and optimal app performance.}
      \resumeItem{\textbf{Integrated Firebase Cloud Storage} for backend storage and implemented push notifications using \textbf{Firebase Cloud Messaging (FCM)}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Project Savings Reporting Transformation} $|$ \emph{DataBricks, ADF, MongoDB, SQL, Tabular Model}}{}
\resumeItemListStart
\resumeItem{\textbf{Designed a metadata-driven reporting framework} to support client-specific Project Savings reporting requirements during the migration from Smart to Quantum.}

\resumeItem{\textbf{Built dynamic ingestion and transformation pipelines} leveraging MongoDB domain models, configuration metadata, and master setup data to generate reporting datasets across diverse client reporting methodologies.}

\resumeItem{\textbf{Delivered a unified reporting solution} capable of supporting multiple savings-calculation and reporting formats through reusable business logic rather than client-specific implementations.}

\resumeItemListEnd

\resumeProjectHeading
{\textbf{Migration Automation for GEP Quantum} $|$ \emph{Python, Power BI, SQL, MongoDB}}{}
\resumeItemListStart
\resumeItem{\textbf{Built a low-touch, low-maintenance migration framework} to automate reporting migrations between Smart and Quantum platforms.}

\resumeItem{\textbf{Developed metadata-driven utilities} that consumed SQL Server configurations and MongoDB domain-model definitions to automate reporting setup, model generation, and environment configuration.}

\resumeItem{\textbf{Implemented intelligent schema-mapping and validation workflows} to reconcile structural differences between platforms while preserving existing report behavior and user experiences.}


\resumeItemListEnd

\resumeProjectHeading
{\textbf{Report Validation \& Data Quality Framework} $|$ \emph{Python, DataBricks, MongoDB, SQL}}{}
\resumeItemListStart
\resumeItem{\textbf{Developed an automated data-quality framework} to validate reporting consistency between Smart and Quantum during migration activities.}

\resumeItem{\textbf{Validated 500+ reports} across \textbf{100+ clients} and \textbf{12+ modules} by comparing report outputs, metadata, and underlying datasets across platforms.}

\resumeItem{\textbf{Identified critical reporting discrepancies and platform defects} prior to production deployments, reducing migration risk and improving reporting reliability.}

\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------EDUCATION-----------

\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {M.Tech. in Computer Science \textnormal}{June. 2028(Expected}
      {\textbf{International Institute of Information Technology (IIITH)}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework}: AI/ML, Probability \& Statistics, Advanced Linear Algebra, Software Systems Development.}
      \resumeItemListEnd

    \resumeSubheading
      {B.E. in Computer Engineering \hfill \textnormal{CGPA: 9.37/10}}{Aug. 2019 -- May 2023}
      {\textbf{Terna Engineering College (University of Mumbai)}}{Navi Mumbai, India}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework}: Data Structures and Algorithms, Database Management And Systems, Big Data Warehousing, Python.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages \& Databases}{: Python, C++, PySpark, SQL, MongoDB} \vspace{2pt} \\
     \textbf{Cloud \& Data Engineering}{: Azure Databricks (ADB), Azure Data Factory (ADF), Delta Lake, ETL Architecture, Data Pipelines, Spark Performance Tuning, SQL Optimization} \vspace{2pt} \\
     \textbf{Tools \& Methodologies}{: Power BI, Git/GitHub, Jira, Requirements Gathering, Data Analysis}
    }}
 \end{itemize}

%-----------ACHIEVEMENTS-----------
\section{ACHIEVEMENTS}
  \resumeItemListStart
    \resumeItem{\textbf{GEP Kudos Achiever Award} (Jul. 2024 -- Sept. 2024): Honored for exceptional technical execution and unwavering dedication to the organization.}
  \resumeItemListEnd

%-----------LANGUAGES \& INTERESTS-----------
\section{LANGUAGES \& INTERESTS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: English, Hindi, Marathi (Full Professional Proficiency)} \hspace{15pt} $|$ \hspace{15pt} \textbf{Interests}{: Chess, Badminton, Reading}
    }}
 \end{itemize}

\end{document}